Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-09-01 manuscript/draft.Rmd
Add citation to Blonder 2017 regarding lags in prediction

The accuracy for forecasts is expected to decline as forecasts are made further
into the future, so it is important to evaluate forecasts at different lead
times [Box 1; @petchey2015]. For deviance (the error metric that evaluates both
models' point estimates and their uncertainty simultaneously), there is some
indication that the JSDM and the nonlinear richness model converge towards the
time-series and baseline models as the lead time of the forecast increases. This
potential convergence is biologically plausible because at short lead times,
environmental changes are relatively small and changes in the biota may lag
behind changes in the environment. However, as the lead time of the forecast
increases the amount of environmental change should increase and the systems
will have more time to respond, potentially resulting in shifts towards improved
relative performance of models incorporating environmental and ecological
information. This is potentially important for interpreting our results because
we only evaluated annual forecasts up to a decade into the future. In contrast,
many ecological forecasts are temporally aggregated to 5-30 year timesteps and
have lead times of up to a century. These long-term forecasts are difficult to
evaluate given the small number of century scale datasets, but are important for
understanding changes in biodiversity at some of the lead times relevant for
conservation and management. Two studies have assessed models of species
richness at longer lead times [@algar2009; @distler2015], but the results were
not compared to baseline or time-series models (in part due to data limitations)
making them difficult to compare to our results. Given the potential changes
with lead time of the models and processes are most relevant to forecasting, it
is important that more long lead time evaluation studies are conducted and that
the inferences drawn from short-term and long-term forecasting studies be
compared. For true forecasts, short term forecasts will allow for relatively
rapid validation of models by researchers without needing to wait decades for
data to accumulate [@tredennick2016; @dietze2016]. However, since drivers of
species richness differ at different temporal scales [@rosenzweig1995;
@white2004; @white2007], short-term forecasts should be viewed as informing, not
replacing, long-term forecasts [@tredennick2016].

>>>>

The accuracy for forecasts is expected to decline as forecasts are made further
into the future, so it is important to evaluate forecasts at different lead
times [Box 1; @petchey2015]. For deviance (the error metric that evaluates both
models' point estimates and their uncertainty simultaneously), there is some
indication that the JSDM and the nonlinear richness model converge towards the
time-series and baseline models as the lead time of the forecast increases. This
potential convergence is biologically plausible because at short lead times,
environmental changes are relatively small and changes in the biota may lag
behind changes in the environment. However, as the lead time of the forecast
increases the amount of environmental change should increase and the systems
will have more time to respond, potentially resulting in shifts towards improved
relative performance of models incorporating environmental and ecological
information [@blonder2017]. This is potentially important for interpreting our
results because we only evaluated annual forecasts up to a decade into the
future. In contrast, many ecological forecasts are temporally aggregated to 5-30
year timesteps and have lead times of up to a century. These long-term forecasts
are difficult to evaluate given the small number of century scale datasets, but
are important for understanding changes in biodiversity at some of the lead
times relevant for conservation and management. Two studies have assessed models
of species richness at longer lead times [@algar2009; @distler2015], but the
results were not compared to baseline or time-series models (in part due to data
limitations) making them difficult to compare to our results. Given the
potential changes with lead time of the models and processes are most relevant
to forecasting, it is important that more long lead time evaluation studies are
conducted and that the inferences drawn from short-term and long-term
forecasting studies be compared. For true forecasts, short term forecasts will
allow for relatively rapid validation of models by researchers without needing
to wait decades for data to accumulate [@tredennick2016; @dietze2016]. However,
since drivers of species richness differ at different temporal scales
[@rosenzweig1995; @white2004; @white2007], short-term forecasts should be viewed
as informing, not replacing, long-term forecasts [@tredennick2016].
